When, why, and how to avoid, prefer, or tolerate inbreeding

### 2018-03-31 presentation/inbreeding.Rmd
More slides

@@

@@

Make point about inbreeding adjustment given strong constraints

>>>>

<center>
![](images/poly_motivation.png)

<center>
![](images/fem_poly_1.png)

<center>
![](images/fem_poly_2.png)

@@

<center>
![](images/inbr_adjust_res0.png)

<center>
![](images/inbr_adjust_res.png)

## Inbreeding adjustment conclusions

1. Selection for females to increase or decrease pre-copulatory inbreeding through multiple mating, [depending on inbreeding depression](https://bradduthie.github.io/DuthieEtAl2016b.pdf#page=11) ($\beta$).
2. Realised inbreeding adjustment ($k_{adj}$) often [small and difficult to detect](https://bradduthie.github.io/DuthieEtAl2016b.pdf#page=11).

</div>
<span style="font-size: 18px;">
Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf).
</span>

## Post-copulatory inbreeding avoidance {.smaller}

<center>
![](images/pre_post_1.png)

## Post-copulatory inbreeding avoidance {.smaller}

<center>
![](images/pre_post_2.png)

## Post-copulatory inbreeding avoidance {.smaller}

<center>
![](images/pre_post_3.png)

@@
